OptiFit: a fast method for fitting amplicon sequences to existing OTUs

### 2021-06-22 paper/paper.Rmd
Just use pdf_document output format

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
authors:
  - name: "Kelly L. Sovacool"
    url: https://github.com/kelly-sovacool
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan
    orcid_id: 0000-0003-3283-829X
  - name: "Sarah L. Westcott"
    url: https://github.com/mothur-westcott
    affiliation: Department of Microbiology and Immunology, University of Michigan
  - name: "M. Brodie Mumphrey"
    url: https://github.com/MBMumphrey
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan
  - name: "Gabrielle A. Dotson"
    url: https://github.com/dotsonga
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan
  - name: "Patrick D. Schloss"
    url: https://github.com/pschloss
    affiliation: Department of Microbiology and Immunology, University of Michigan
bibliography: references.bib
output:
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
  bookdown::pdf_document2:
    keep_tex: false
    includes:
      in_header: preamble.tex
      before_body: head.tex
      after_body: tail.tex
    number_sections: false
    toc: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
creative_commons: CC BY-SA
twitter:
  creator: "@kelly_sovacool"
  site: "@PatSchloss"
---

@@

## Acknowledgements {.appendix}

@@

## Author Contributions {.appendix}

@@

>>>>

---
title: "OptiFit: a fast method for fitting amplicon sequences to existing OTUs"
date: '`r Sys.Date()`'
bibliography: references.bib
output:
  pdf_document:
    keep_tex: false
    includes:
      in_header: preamble.tex
      before_body: head.tex
    number_sections: false
    toc: false
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/OptiFitAnalysis
---

@@

## Acknowledgements

@@

## Author Contributions

@@

## References
